\documentclass{dissertation}

%% Turn off page numbering for the propositions and make the margins on both
%% sides equal and symmetrical.
\geometry{twoside=false}
\pagestyle{empty}

\begin{document}

%% Specify the title and author of the thesis. This information will be used on
%% both the English and Dutch side and in the metadata of the final PDF.
\title[Bulk Formulas and Process Based Models]{Longshore Sediment Transport}
\author{João}{Mil-Homens}

\begin{center}

{\Large\titlefont\bfseries Propositions}

\bigskip

accompanying the dissertation

\bigskip

%% Print the title.
{\makeatletter
\titlestyle\bfseries\large\@title
\makeatother}

%% Print the optional subtitle.
{\makeatletter
\ifx\@subtitle\undefined\else
    \titlefont\titleshape\@subtitle
\fi
\makeatother}

\bigskip

by

\bigskip

%% Print the full name of the author.
\makeatletter
{\large\titlefont\bfseries\@firstname\ {\titleshape\@lastname}}
\makeatother

\end{center}

\bigskip
\bigskip

\begin{enumerate}

\item The influence of the wave breaking types needs to be taken into account when estimating Longshore Sediment Transport rates. - this thesis
\item In some places tidal variation may be an important factor influencing Longshore Sediment Transport  rates and should  therefore be further investigated. - this thesis
\item Tweaking the beach profile may delay or accelerate Longshore Sediment Transport rates. - this thesis
\item There are plenty of sediment concentration data, except, of course, at the location one needs the most.
\item Success is 1\% inspiration, 49\% perspiration and about 50\% luck.

\item Laziness is an important driver of progress.
\item A simple model with plenty of data to calibrate and to validate it is preferable to the most sophisticated model and fewer data.

\item There is no better way to understand numerical modelling than to build one model, as simple as it may be.
\item The Dunning-Kruger effect is one of the main threats to progress of society.
\item To be a good researcher one must strike a fine balance between overconfidence (or even arrogance) and respect for authority.
\end{enumerate}

\bigskip
\bigskip

%% Apart from the name and title of the supervisor, the following text is
%% dictated by the promotieregelement.
\begin{center}
These propositions are regarded as opposable and defendable, and have been approved as such by the supervisors prof.\ dr.\ ir.\ M.J.F.\ Stive and prof.\ dr.\ ir.\ A.J.H.M.\ Reniers
\end{center}

\clearpage
{\selectlanguage{dutch}

\begin{center}

{\Large\titlefont\bfseries Stellingen}

\bigskip

behorende bij het proefschrift

\bigskip

%% Print the title.
{\makeatletter
\titlestyle\bfseries\large\@title
\makeatother}

%% Print the optional subtitle.
{\makeatletter
\ifx\@subtitle\undefined\else
    \titlefont\titleshape\@subtitle
\fi
\makeatother}

\bigskip

door

\bigskip

%% Print the full name of the author.
\makeatletter
{\large\titlefont\bfseries\@firstname\ {\titleshape\@lastname}}
\makeatother

\end{center}

\bigskip
\bigskip

\begin{enumerate}

\item Bij het inschatten van het kustlangs sedimenttransport moet rekening worden gehouden met de invloed van het type  golfbreker. - Dit proefschrift
\item Variaties in het getij kunnen een belangrijke factor van invloed zijn op kustlangs sedimenttransport en moeten verder worden onderzocht. - Dit proefschrift
\item Aanpassing van het strand profiel kan het kustlangs sedimenttransport vertragen of versnellen. – Dit proefschrift
\item Er zijn voldoende gegevens van sediment concentratie, behalve, natuurlijk, op de locatie waar deze het meest nodig zijn.
\item Succes is 1\% inspiratie, 49\% transpiratie en ongeveer 50\% geluk.
\item Luiheid is een belangrijke drijfveer van vooruitgang.
\item Een eenvoudig model met voldoende te kalibreren en te valideren gegevens, is te verkiezen boven het meest geavanceerde model met minder gegevens.
\item Er is geen betere manier om numerieke modellering te begrijpen, dan om een zo eenvoudig mogelijk model te bouwen.
\item Het Dunning-Kruger effect is een van de belangrijkste bedreigingen voor de vooruitgang van de samenleving.
\item Om een goede onderzoeker te zijn, moet men een goed evenwicht vinden tussen overmoedigheid (of zelfs arrogantie) en respect voor autoriteit .

\end{enumerate}

\bigskip
\bigskip

%% Apart from the name and title of the supervisor, the following text is
%% dictated by the promotieregelement.
\begin{center}
Deze stellingen worden opponeerbaar en verdedigbaar geacht en zijn als zodanig goedgekeurd door de promotoren, prof.\ dr.\ ir.\ M.J.F.\ Stive en prof.\ dr.\ ir.\ A.J.H.M.\ Reniers.
\end{center}

}

\end{document}

